Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
style edit: replacing 0 \leq t < T with t \in [0,T], and removing sup sup

	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $t \mapsto u_t^{b_2}$ is increasing and 
	$$ \sup_{b_2 \geq b_2^{*,u,upper}} \sup_{0\leq t \leq T} \left\{ u_t^{b_2} \right\} = \sup_{b_2 \geq b_2^{*,u,upper}} \left\{ u_T^{b_2}\right\}  = \sup_{b_2 \geq b_2^{*,u,upper}} \{ D^{u,b_2}  \} \leq D^{u,b_2 \to \infty} + 1.$$
	Thus,
	\begin{equation*}
	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper}.
	\label{eq:u_t_bound}
	\end{equation*}
	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that
	\begin{equation}
	\sup_{b_2 \geq b_2^{*,upper}} \sup_{0 \leq t \leq T} \max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M,
	\label{eq:ut_wt_upper_bound_b2_infty}
	\end{equation}
	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$.

@@

\begin{proof}
	% case when b2 bar \to infty
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0, \quad B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $0 \leq t < T$:
	\begin{equation*}
	\begin{array}{l}
	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}

	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$. Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$. Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	\begin{equation}
	\left\vert u_t^{\bar{b}_2} \right\vert 
	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 3 c_{\delta_u^{\bar{b}_2 \to \infty}} + 1.
	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
	\end{equation}
	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,upper}$, 
	\begin{equation}
	\sup_{\bar{b}_2 \geq \bar{b}_2^{*,upper}} \sup_{t \in [0,T]} \max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M.
	\label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
	\end{equation}
	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$. Denote $\zeta: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$. Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
	\begin{equation}
	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} } 
	\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
	\label{eq:ut_lower_bound_b2_bar_infty}
	\end{equation}

@@

	% case 4: b1 bar to infinity
	\textbf{Case 4:} Now, consider $\bar{b}_1 \to \infty$.
	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
	\begin{equation*}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty, \quad -\delta^{-,\bar{b}_1}_u=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,
	\end{equation*}
	\begin{equation*}
	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1.
	\end{equation*}
	We also have for $t\in [0,T)$:
	$$\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
	\xrightarrow[\bar{b}_1 \to \infty]{}0,$$
	which implies:
	$
	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
	$
	Therefore, for $t \in [0,T)$:
	$\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}$. By the same arguments, we have for $t \in [0,T)$: $\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}$.

>>>>

	From equation (\ref{eq:riccati_ut_sol_deriv}), we see that $t \mapsto u_t^{b_2}$ is increasing if $B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} > 0$. Since 
	$\lim_{b_2 \to \infty} B^{b_2} (D^{u,b_2})^2 + 2 A^u D^{u,b_2} - C^{u,b_2} = \infty,$ there exists $b_2^{*,u,upper} >0$ such that for all $b_2 \geq b_2^{*,u,upper}$, we have $|D^{u,b_2} -D^{u,b_2 \to \infty} | \leq 1$ and $t \mapsto u_t^{b_2}$ is increasing and thus, $ u_t^{b_2}\leq u_T^{b_2} = D^{u,b_2} \leq D^{u,b_2 \to \infty} + 1.$
	Therefore,
	\begin{equation*}
	\left\vert u_t^{b_2}\right\vert \leq D^{u,b_2 \to \infty} + 1 , \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,u,upper}.
	\label{eq:u_t_bound}
	\end{equation*}
	By the same argument for $w_t^{b_2}$ and $\eta_t^{b_2}$, there exists $b_2^{*,upper} \geq b_2^{*,u,upper}$ such that:
	\begin{equation}
	\max \left\{ \vert u_t^{b_2} \vert , \vert w_t^{b_2} \vert, \vert \eta_t^{b_2} \vert \right\} \leq M, \quad \forall \  t\in[0,T],\ b_2 \geq b_2^{*,upper},
	\label{eq:ut_wt_upper_bound_b2_infty}
	\end{equation}
	and the functions $t \mapsto u_t^{b_2}$, $t \mapsto w_t^{b_2}$ and $t \mapsto \eta_t^{b_2}$ are increasing on $[0,T]$.

@@

\begin{proof}
	% case when b2 bar \to infty
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0, \quad B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $t \in [0,T)$:
	\begin{equation*}
	\begin{array}{l}
	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}

	Next, we provide a uniform upper bound for $u_t^{\bar{b}_2}$ over $[0,T]$ and large $\bar{b}_2$. Let $\zeta_1 := \frac{1}{2} \min \left\{ c_{\delta_u^{\bar{b}_2 \to \infty}}, \  c_{\delta_w^{\bar{b}_2 \to \infty} } \right\}$. Then there exists $\bar{b}_2^{*,u} >0 $ such that for all $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	$$ \max\left\{ \left\vert \frac{\delta_u^{+,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - c_{\delta^{\bar{b}_2 \to \infty}_u} \right\vert , \ \left\vert \frac{\delta_u^{-,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} - (-c_{\delta^{\bar{b}_2 \to \infty}_u})\right\vert,\    \left\vert \frac{C^{u,\bar{b}_2}}{\sqrt{b_2 + \bar{b}_2}} \right\vert, \   \left\vert D^{u,\bar{b}_2} \right\vert, \  \frac{1}{\sqrt{b_2 + \bar{b}_2}}  \right\} \leq \zeta_1. $$ 
	Then with equation (\ref{eq:riccati_ut_sol}), for any $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$,
	\begin{equation}
	\left\vert u_t^{\bar{b}_2} \right\vert 
	\leq \frac{C^{u,\bar{b}_2}+ D^{u,\bar{b}_2} \left(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2} \right)}{- \delta_u^{-,\bar{b}_2}} \\
	\leq  \frac{\zeta_1 + \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1)}{ c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1} \leq 3 c_{\delta_u^{\bar{b}_2 \to \infty}} + 1.
	\label{eq:ut_uniform_upper_bound_b2_bar_infinity}
	\end{equation}
	By the same argument for $w_t^{b_2}$ and together with inequality (\ref{eq:ut_uniform_upper_bound_b2_bar_infinity}), there exists $\bar{b}_2^{*,upper} \geq \bar{b}_2^{*,u}$ and $M>0$ such that:
	\begin{equation}
	\max \left\{ \vert u_t^{\bar{b}_2}\vert, \vert w_t^{\bar{b}_2} \vert \right\} \leq M, \quad \forall t \in[0,T],\ \bar{b}_2 \geq \bar{b}_2^{*,upper} .
	\label{eq:ut_wt_uniform_upper_bound_b2_bar_infty}
	\end{equation}
	Furthermore, we can get a uniform lower bound for $(b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2}$. Denote $\zeta: = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) (q_T + \bar{q}_T(1-s_T))}{r + \bar{r}(1-s)}$. Then for all $t \in [0,T]$ and $\bar{b}_2 \geq \bar{b}_2^{*,u}$ we have:
	\begin{equation}
	\left\vert (b_2 + \bar{b}_2)^{\frac{3}{2}} u_t^{\bar{b}_2} \right\vert \geq    \frac{ (b_2 + \bar{b}_2)^{\frac{3}{2}} \cdot D^{u,\bar{b}_2} \delta_u^{+,\bar{b}_2}}{(\delta_u^{+,\bar{b}_2} - \delta_u^{-,\bar{b}_2}) + B^{\bar{b}_2} D^{u,\bar{b}_2} } 
	\geq  \frac{\zeta (c_{\delta_u^{\bar{b}_2 \to \infty}} - \zeta_1)}{ \zeta_1 (2 c_{\delta_u^{\bar{b}_2 \to \infty}} + 2 \zeta_1) + \zeta / (r+ \bar{r}(1-\bar{s})^2) } =: m_u.
	\label{eq:ut_lower_bound_b2_bar_infty}
	\end{equation}

@@

	% case 4: b1 bar to infinity
	\textbf{Case 4:} Now, consider $\bar{b}_1 \to \infty$.
	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
	\begin{equation*}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty, \quad -\delta^{-,\bar{b}_1}_u=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,
	\end{equation*}
	\begin{equation*}
	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1.
	\end{equation*}
	We also have for $t\in [0,T)$:
	$$\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
	\xrightarrow[\bar{b}_1 \to \infty]{}0,$$
	which implies:
	$
	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
	$
	Therefore, for $t \in [0,T)$:
	$\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}$. By the same argument, we have for $t \in [0,T)$: $\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}$.
